---
title: "Practical homework 2"
output: html_document
date: "2025-04-13"
---

```{r setup, include=FALSE}
# Load libraries ----------------------------------------------------------
library(tidyverse)
library(caret)

# Load data ---------------------------------------------------------------

load('/Users/joshuawilkes/Desktop/NSDUH_2023.Rdata')
NSDUH_2023 = puf2023_102124

NSDUH_2023
# Select only variables of interest -------------------------------------------

# select those that answered the youth experiences questions
dfo <- NSDUH_2023[!is.na(NSDUH_2023$SCHFELT),]

# make a vector of substance use column names
substance_cols <- c(   # quantitative values for frequency of use
                       'iralcfy', # alcohol frequency past year (1-365)
                       'irmjfy', # marijuana frequency past year (1-365)
                       'ircigfm', #cigarette frequency past month (1-30)
                       'IRSMKLSS30N', # smokeless tobacco frequency past month (1-30)
                       'iralcfm', # alcohol frequency past month (1-30)
                       'irmjfm', # marijuana frequency past month (1-30)
                       
                       # quantitative values for age of first use
                       'ircigage', # cigarette age of first use (1-55), 991=never used
                       'irsmklsstry', # smokeless tobacco age of first use (1-70), 991=never used
                       'iralcage', # alcohol age of first use (1-66), 991=never used
                       'irmjage', # marijuana age of first use (1-83), 991=never used
                       
                       # binary categories for use at all
                       'mrjflag', # marijuana ever used (0=never, 1=ever)
                       'alcflag', # alcohol ever used (0=never, 1=ever)
                       'tobflag', # any tobacco ever used (0=never, 1=ever)
                       
                       # multiclass categories for frequency of use 
                       'alcydays', # number of days of alcohol in past year (1-5 categories, 6=none)
                       'mrjydays', # number of days of marijuana in past year (1-5 categories, 6=none)
                       'alcmdays', # number of days of alcohol in past month (1-4 categories, 5=none)
                       'mrjmdays', # number of days of marijuana in past month (1-4 categories, 5=none)
                       'cigmdays', # number of days of cigarettes in past month (1-5 categories, 6=none)
                       'smklsmdays' # number of days of smokeless tobacco in past month (1-4 categories, 5=none)
                      ) %>% toupper()

# make a vector of demographic column names ------------------------
demographic_cols <- c(
                  'irsex', # binary sex (1=male, 2=female)
                  'NEWRACE2', # race (7 categories)
                  'HEALTH2', # overall health (4 categories)
                  'eduschlgo', # now going to school (1=yes, 2=no)
                  'EDUSCHGRD2', # what grade in now/will be in (11 categories, 98,99= blank/skip)
                  'eduskpcom', #how many days skipped school in past month (1-30, 94/97/98/99=blank/skip)
                  'imother', # for youth, mother in household (1=yes, 2=no, 3=don't know, 4=over 18)
                  'ifather', # for youth, father in household (1=yes, 2=no, 3=don't know, 4=over 18)
                  'income', # total family income (4 categories)
                  'govtprog', # got gov assistance (1=yes, 2=no)
                  'POVERTY3', # poverty level (4 categories)
                  'PDEN10', # population density (1= >1M people, 2=<1M people, 3=can't be determined)
                  'COUTYP4' # metro size status (1=large metro, 2=small metro, 3=nonmetro)
                  ) %>% toupper()

# select columns of interest
df_youth <- dfo %>% select(SCHFELT:RLGFRND) # use all youth questions, start with schfelt and go through rlgfrnd
df_substance <- dfo %>% select(substance_cols) # select specific substance columns of interest
df_demog <- dfo %>% select(demographic_cols)  # select specific demographic columns of interest

# combine into one data frame
df = cbind(df_substance, df_youth, df_demog) #combine into one data frame

# Fix metadata ------------------------------------------------------------

# make vector of columns from the data that should be converted to factors, unordered and ordered
unordered_factor_cols <- c(names(df_youth), # all columns from youth
                           'mrjflag','alcflag','tobflag', # binary flag columns from substance
                           'irsex','NEWRACE2','eduschlgo','imother','ifather','govtprog','PDEN10','COUTYP4' # unordered categories for demographics
                           ) %>% toupper()
ordered_factor_cols <- c('EDUSCHGRD2','HEALTH2','POVERTY3','income') %>% toupper()

# convert to factors
df[unordered_factor_cols] <- lapply(df[unordered_factor_cols], factor) # correct columns to unordered factors (e.g. yes, no)
df[ordered_factor_cols] <- lapply(df[ordered_factor_cols], factor, ordered=TRUE) # correct columns to ordered factors (e.g. small, medium, large)

# fix variable label metadata to only include the selected columns
new_labels <- attr(dfo,'var.labels')[match(names(df), attr(dfo,'names'))]
attr(df,'var.labels') <- new_labels

# note: use attr(df,'var.labels') to see the labeled data

youth_experience_cols = names(df_youth)

# Save cleaned data ------------------------
save(df, youth_experience_cols, substance_cols, demographic_cols, file = 'youth_data.Rdata')

youth <- read.csv("/Users/joshuawilkes/Desktop/youth_data.csv")

```



What are the predictors for if a youth has smoked cigarettes

Found two predictors that appear to correlate to whether an applicant was found to have a history of smoking cigarettes. Looking over the demographic columns used, two predictors were found with what grade surveyee will be and what what their overall health score was. with a higher health score indicating a higher chance of smoking and later grades being seen as more likely this decision tree was found to have an 8.9% training error and a 9.4% test error


```{r include=TRUE}

set.seed(1)
library(tree)
library(magrittr)
library(rpart)
library(rpart.plot) # or library(dplyr)
demographic_cols <- c(
  'irsex',      # binary sex (1=male, 2=female)
  'NEWRACE2',   # race (7 categories)
  'HEALTH2',    # overall health (4 categories)
  'eduschlgo',  # now going to school (1=yes, 2=no)
  'EDUSCHGRD2', # current/will be in what grade (11 categories, 98,99= blank/skip)
  'eduskpcom',  # days skipped school in past month (1-30, 94/97/98/99=blank/skip)
  'imother',    # for youth, mother in household (1=yes, 2=no, 3=don't know, 4=over 18)
  'ifather',    # for youth, father in household (1=yes, 2=no, 3=don't know, 4=over 18)
  'income',     # total family income (4 categories)
  'govtprog',   # got government assistance (1=yes, 2=no)
  'POVERTY3',   # poverty level (4 categories)
  'PDEN10',     # population density (1= >1M people, 2=<1M people, 3=can't be determined)
  'COUTYP4'     # metro size status (1=large metro, 2=small metro, 3=nonmetro)
) %>% toupper()

demographic_cols

#setting up training and testing set
cig.id = sample(1:nrow(youth), nrow(youth)/3)
cig.train = youth[-cig.id,]
cig.test = youth[cig.id,]
cig.train$TOBFLAG <- as.factor(cig.train$TOBFLAG)
cig.test$TOBFLAG <- as.factor(cig.test$TOBFLAG)

#using demographics to find possible predictors of tobacco use
formula_str <- paste("TOBFLAG ~", paste(demographic_cols, collapse = " + "))
tree_formula <- as.formula(formula_str, )
cig.tree <- tree(tree_formula, data = cig.train)

#visualization


#finding test error
cig.pred <- predict(cig.tree, cig.test, type = "class")

cig.table = table(cig.pred, cig.test$TOBFLAG)
cig.table

(cig.table[1,2]+cig.table[2,1])/sum(cig.table)
cig_test_error <- (cig.table[1,2]+cig.table[2,1])/sum(cig.table) * 100
cig_test_error

```
continuing investigating using random forest and bagging to find a more accurate model

```{r include=TRUE}
library(randomForest)
library(gbm)
set.seed(2)
#cleaning training data of NA values
cig.id = sample(1:nrow(youth), nrow(youth)/3)
cig.train = youth[-cig.id,]
cig.test = youth[cig.id,]
cig.train$TOBFLAG <- as.factor(cig.train$TOBFLAG)
cig.test$TOBFLAG <- as.factor(cig.test$TOBFLAG)

cig.train_clean <- na.omit(cig.train)
cig.test_clean <- na.omit(cig.test)



#using bagging
cig.bag <- randomForest(TOBFLAG ~ ., data = cig.train_clean[, c("TOBFLAG", demographic_cols)], mtry = length(demographic_cols), importance = TRUE, ntree = 100)

Cigarette_Usage <- cig.bag
plot(Cigarette_Usage)

yhat.cig.bag <- predict(cig.bag, newdata =cig.test_clean)
cig.bag.mean.error <- mean((yhat.cig.bag!= cig.test$TOBFLAG))
cig.bag.mean.error
summary(cig.bag)
varImpPlot(cig.bag)
importance(cig.bag)

bag_importance <- importance(cig.bag)

#visualization
if ("MeanDecreaseGini" %in% colnames(bag_importance)) {
  bag_importance_df <- data.frame(
    Variable = rownames(bag_importance),
    MeanDecreaseGini = bag_importance[, "MeanDecreaseGini"]
  )
  
  # Descriptive labels for demographics
  descriptive_labels <- c(
    IRSEX = "Sex",
    NEWRACE2 = "Race",
    HEALTH2 = "General Health",
    EDUSCHLGO = "School Enrollment",
    EDUSCHGRD2 = "Grade Level",
    EDUSKPCOM = "days skipped school",
    IMOTHER = "Lives with Mother",
    IFATHER = "Lives with Father",
    INCOME = "Household Income",
    GOVTPROG = "Government Assistance",
    POVERTY3 = "Poverty Level",
    PDEN10 = "Population Density",
    COUTYP4 = "County Type"
  )



  bag_importance_df$DescriptiveName <- descriptive_labels[bag_importance_df$Variable]
  
 
  bag_importance_df$DescriptiveName[is.na(bag_importance_df$DescriptiveName)] <- bag_importance_df$Variable[is.na(bag_importance_df$DescriptiveName)]

 
  bag_importance_df <- bag_importance_df[order(bag_importance_df$MeanDecreaseGini, decreasing = TRUE), ]
  
  
  
  # Plot
  library(ggplot2)
  ggplot(bag_importance_df, aes(x = reorder(DescriptiveName, MeanDecreaseGini), y = MeanDecreaseGini)) +
    geom_col(fill = "#7570b3") +
    coord_flip() +
    labs(
      title = "History of Cigarette Use (Bagging Model)",
      subtitle = "Measured by Mean Decrease in Gini",
      x = "Demographic Variable",
      y = "Importance Score"
    ) +
    theme_minimal(base_size = 14)
  
} else {
  print("MeanDecreaseGini column not found in importance output.")
}



```
Using random forest for the history of cigarette use
```{r}
set.seed(2)
#cleaning training data of NA values
cig.id = sample(1:nrow(youth), nrow(youth)/3)
cig.train = youth[-cig.id,]
cig.test = youth[cig.id,]
cig.train$TOBFLAG <- as.factor(cig.train$TOBFLAG)
cig.test$TOBFLAG <- as.factor(cig.test$TOBFLAG)

cig.train_clean <- na.omit(cig.train)
cig.test_clean <- na.omit(cig.test)

#tuning for optimal mtry number
rf_control <- trainControl(method = "cv", number = 5)
rf_grid <- expand.grid(
  mtry = c(2, 4, 6, 8, 10)  # adjust based on number of predictors
)

#using random forest with predictors found using decision tree
cig.rf <- randomForest(TOBFLAG ~ ., data = cig.train_clean[, c("TOBFLAG", demographic_cols)], mtry = 3, ntree = 100, importance = TRUE, trControl = rf_control, tuneGrid = rf_grid)

Cigarette_Usage_RF <- cig.rf
plot(Cigarette_Usage_RF)

yhat.cig.rf <- predict(cig.rf, newdata =cig.test_clean)
cig.rf.mean.error <- mean((yhat.cig.rf!= cig.test$TOBFLAG))
cig.rf.mean.error
summary(cig.bag)
varImpPlot(cig.bag)
importance(cig.bag)

bag_importance <- importance(cig.bag)

#Visualization
if ("MeanDecreaseGini" %in% colnames(bag_importance)) {
  bag_importance_df <- data.frame(
    Variable = rownames(bag_importance),
    MeanDecreaseGini = bag_importance[, "MeanDecreaseGini"]
  )
  
  # Descriptive labels for demographics
  descriptive_labels <- c(
    IRSEX = "Sex",
    NEWRACE2 = "Race",
    HEALTH2 = "General Health",
    EDUSCHLGO = "School Enrollment",
    EDUSCHGRD2 = "Grade Level",
    EDUSKPCOM = "days skipped school",
    IMOTHER = "Lives with Mother",
    IFATHER = "Lives with Father",
    INCOME = "Household Income",
    GOVTPROG = "Government Assistance",
    POVERTY3 = "Poverty Level",
    PDEN10 = "Population Density",
    COUTYP4 = "County Type"
  )


  bag_importance_df$DescriptiveName <- descriptive_labels[bag_importance_df$Variable]
  
 
  bag_importance_df$DescriptiveName[is.na(bag_importance_df$DescriptiveName)] <- bag_importance_df$Variable[is.na(bag_importance_df$DescriptiveName)]

  
  bag_importance_df <- bag_importance_df[order(bag_importance_df$MeanDecreaseGini, decreasing = TRUE), ]
  
  
  
  # Plot
  library(ggplot2)
  ggplot(bag_importance_df, aes(x = reorder(DescriptiveName, MeanDecreaseGini), y = MeanDecreaseGini)) +
    geom_col(fill = "#7570b3") +
    coord_flip() +
    labs(
      title = "History of Cigarette Use (Random Forest)",
      subtitle = "Measured by Mean Decrease in Gini",
      x = "Demographic Variable",
      y = "Importance Score"
    ) +
    theme_minimal(base_size = 14)
  
} else {
  print("MeanDecreaseGini column not found in importance output.")
}


```


Looking into number of cigarettes smoked per month in the survey

```{r include=TRUE}
library(vip)

youth$CIGUSE_LEVEL <- factor(youth$CIGMDAYS,
  levels = 1:6,
  labels = c("1-2 days", "3-5 days", "6-9 days", "10-19 days", "20-29 days", "None")
)
youth_clean <- youth[!is.na(youth$CIGMDAYS), ]

set.seed(3)
cig.id = sample(1:nrow(youth_clean), nrow(youth_clean)/3)
cig.train = youth_clean[-cig.id,]
cig.test = youth_clean[cig.id,]

cig.train_clean <- na.omit(cig.train)
cig.test_clean <- na.omit(cig.test)

demographic_cols



#using demographics to find possible predictors of tobacco use
formula_str <- paste("CIGUSE_LEVEL ~", paste(demographic_cols, collapse = " + "))
tree_formula <- as.formula(formula_str)
cig.tree <- tree(tree_formula, data = cig.train)

#visualization
summary(cig.tree)
plot(cig.tree)
text(cig.tree, pretty = 0)

#finding test error
cig.pred <- predict(cig.tree, cig.test, type = "class")

conf_mat <- table(Predicted = cig.pred, Actual = cig.test$CIGUSE_LEVEL)
print(conf_mat)

cig.table = table(cig.pred, cig.test$CIGUSE_LEVEL)
cig.table

accuracy <- 100 * (1 - mean(cig.pred == cig.test$CIGUSE_LEVEL))
accuracy


demographic_cols

#because decision tree largley had "none" as a factor we try random forest and boosting

#tuning for optimal mtry number
rf_control <- trainControl(method = "cv", number = 5)
rf_grid <- expand.grid(
  mtry = c(2, 4, 6, 8, 10)  # adjust based on number of predictors
)

cig.rf <- randomForest(CIGUSE_LEVEL ~ ., data = cig.train_clean[, c("CIGUSE_LEVEL", demographic_cols)], mtry = 3, ntree = 1000, importance = TRUE, trControl = rf_control, tuneGrid = rf_grid)

Cigarette_Usage_Per_Month <- cig.rf

plot(Cigarette_Usage_Per_Month)


yhat.cig.rf <- predict(cig.rf, newdata =cig.test_clean)
cig.rf.mean.error <- mean((yhat.cig.rf!= cig.test$TOBFLAG))
cig.rf.mean.error

pred.rf <- predict(cig.rf, cig.test)
table(Predicted = pred.rf, Actual = cig.test$CIGUSE_LEVEL)


#visualization
descriptive_labels <- c(
    IRSEX = "Sex",
    NEWRACE2 = "Race",
    HEALTH2 = "General Health",
    EDUSCHLGO = "School Enrollment",
    EDUSCHGRD2 = "Grade Level",
    EDUSKPCOM = "days skipped school",
    IMOTHER = "Lives with Mother",
    IFATHER = "Lives with Father",
    INCOME = "Household Income",
    GOVTPROG = "Government Assistance",
    POVERTY3 = "Poverty Level",
    PDEN10 = "Population Density",
    COUTYP4 = "County Type"
)


importance_df <- as.data.frame(importance(cig.rf))
importance_df$Variable <- rownames(importance_df)


importance_df$DescriptiveName <- descriptive_labels[importance_df$Variable]


importance_df$DescriptiveName[is.na(importance_df$DescriptiveName)] <- importance_df$Variable[is.na(importance_df$DescriptiveName)]


importance_df <- importance_df[order(importance_df$MeanDecreaseGini, decreasing = TRUE), ]

# plot
library(ggplot2)
ggplot(importance_df, aes(x = reorder(DescriptiveName, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Cigarette Use Frequency per month (Catagorical)",
    subtitle = "Measured by Mean Decrease in Gini Index",
    x = "Demographic Predictor",
    y = "Importance Score"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    axis.title = element_text(size = 13),
    axis.text = element_text(size = 12)
  )

```

looking at days usuing cigarettes over the past month


```{r include=TRUE}

library(partykit)
library(tree)
library(rpart)
library(party)


youth_clean$IRALCFY[youth_clean$IRALCFY >= 370] <- NA
youth_clean <- youth_clean[!is.na(youth_clean$IRALCFY), ]

# Split into training and testing sets
set.seed(32)
train_idx <- sample(1:nrow(youth_clean), nrow(youth_clean) * 2/3)
train_data <- youth_clean[train_idx, ]
test_data <- youth_clean[-train_idx, ]

# Define formula with demographic predictors
formula_str <- paste("IRALCFY ~", paste(demographic_cols, collapse = " + "))
tree_formula <- as.formula(formula_str)

# Create mapping for descriptive labels
descriptive_labels <- c(
    IRSEX = "Sex",
    NEWRACE2 = "Race",
    HEALTH2 = "General Health",
    EDUSCHLGO = "School Enrollment",
    EDUSCHGRD2 = "Grade Level",
    EDUSKPCOM = "days skipped school",
    IMOTHER = "Lives with Mother",
    IFATHER = "Lives with Father",
    INCOME = "Household Income",
    GOVTPROG = "Government Assistance",
    POVERTY3 = "Poverty Level",
    PDEN10 = "Population Density",
    COUTYP4 = "County Type"
)

# Visualization
cig_rpart <- rpart(tree_formula, data = train_data, method = "anova")


is_var <- cig_rpart$frame$var != "<leaf>"
cig_rpart$frame$var[is_var] <- descriptive_labels[cig_rpart$frame$var[is_var]]


cig_party <- as.party(cig_rpart)

# Plot the decision tree with descriptive labels
plot(cig_party,
     main = "Decision Tree for Alcohol Consumption Over the Past Year",
     tp_args = list(id = FALSE))


```
```{r}
youth_clean$IRALCFY[youth_clean$IRALCFY >= 370] <- NA
youth_clean <- youth_clean[!is.na(youth_clean$IRALCFY), ]

set.seed(32)
train_idx <- sample(1:nrow(youth_clean), nrow(youth_clean) * 2/3)
train_data <- youth_clean[train_idx, ]
test_data <- youth_clean[-train_idx, ]

# using random forest on the dataset
formula_str <- paste("IRALCFY ~", paste(demographic_cols, collapse = " + "))
tree_formula <- as.formula(formula_str)

# Remove rows with any NA in the model variables
model_data <- youth_clean[, c("IRALCFY", demographic_cols)]
model_data <- na.omit(model_data)

# Train/test split
set.seed(32)
train_idx <- sample(1:nrow(model_data), nrow(model_data) * 2/3)
train_data <- model_data[train_idx, ]
test_data <- model_data[-train_idx, ]

library(randomForest)

rf_control <- trainControl(method = "cv", number = 3)
rf_grid <- expand.grid(
  mtry = c(2, 4, 6)  # adjust based on number of predictors
)

set.seed(123)
rf_model <- randomForest(tree_formula, data = train_data, ntree = 1000, importance = TRUE,  trControl = rf_control, tuneGrid = rf_grid)

Alcohol_Usage_RF <- rf_model
plot(Alcohol_Usage_RF)

# Predict
rf_preds <- predict(rf_model, newdata = test_data)

# Calculate RMSE
rmse <- sqrt(mean((rf_preds - test_data$IRALCFY)^2))
print(paste("Random Forest RMSE:", round(rmse, 2)))


importance_values <- importance(rf_model)  # This gives %IncMSE and IncNodePurity
importance_df <- data.frame(Variable = rownames(importance_values),
                            IncNodePurity = importance_values[, "IncNodePurity"],
                            row.names = NULL)

# Define readable names for demographic variables
readable_names <- c(
  IRSEX = "Sex",
  NEWRACE2 = "Race/Ethnicity",
  HEALTH2 = "Self-Reported Health",
  EDUSCHLGO = "School Enrollment",
  EDUSCHGRD2 = "Grade Level",
  EDUSKPCOM = "Days skipped",
  IMOTHER = "Mother's Presence",
  IFATHER = "Father's Presence",
  INCOME = "Household Income",
  GOVTPROG = "Gov't Program Use",
  POVERTY3 = "Poverty Level",
  PDEN10 = "Population Density",
  COUTYP4 = "County Type"
)

# Map readable names
importance_df$Readable <- ifelse(importance_df$Variable %in% names(readable_names),
                                 readable_names[importance_df$Variable],
                                 importance_df$Variable)

# Plot
library(ggplot2)

ggplot(importance_df, aes(x = reorder(Readable, IncNodePurity), y = IncNodePurity)) +
  geom_bar(stat = "identity", fill = "darkorange") +
  coord_flip() +
  labs(title = "Alcohol use per year (Random Forest)",
       x = "Demographic Variables",
       y = "Increase in Node Purity") +
  theme_minimal(base_size = 14)
```


```{r}
library(gbm)
youth_clean$IRALCFY[youth_clean$IRALCFY >= 370] <- NA
youth_clean <- youth_clean[!is.na(youth_clean$IRALCFY), ]

set.seed(42)
cig_boost <- gbm(
  formula = tree_formula,
  data = train_data,
  distribution = "gaussian",  # For regression
  n.trees = 200,
  interaction.depth = 3,
  shrinkage = 0.01,
  cv.folds = 5
)

library(caret)
library(gbm)

set.seed(42)

gbm_grid <- expand.grid(
  n.trees = c(100, 500, 1000),
  interaction.depth = c(2, 4, 6),
  shrinkage = c(0.01, 0.05, 0.1),
  n.minobsinnode = c(5, 10)
)

ctrl <- trainControl(method = "cv", number = 5)

gbm_tuned <- train(
  IRALCFY ~ .,  # Replace with your formula
  data = train_data,
  method = "gbm",
  trControl = ctrl,
  verbose = FALSE,
  tuneGrid = gbm_grid
)

print(gbm_tuned)
plot(gbm_tuned)



# Hyperparameter tuning for Plot performance (cross-validated error)
plot(cig_boost)
best_iter <- gbm.perf(cig_boost, method = "cv")

# Predict on test data
boost_preds <- predict(cig_boost, newdata = test_data, n.trees = best_iter)

# Evaluate with RMSE
rmse <- sqrt(mean((boost_preds - test_data$IRALCFY)^2))
print(paste("Boosting RMSE:", round(rmse, 2)))


#visualization
readable_names <- c(
  IRSEX = "Sex",
  NEWRACE2 = "Race/Ethnicity",
  HEALTH2 = "Self-Reported Health",
  EDUSCHLGO = "School Enrollment",
  EDUSCHGRD2 = "Grade Level",
  EDUSKPCOM = "Days Skipped School",
  IMOTHER = "Mother Present",
  IFATHER = "Father Present",
  INCOME = "Household Income",
  GOVTPROG = "Gov't Program Use",
  POVERTY3 = "Poverty Level",
  PDEN10 = "Population Density",
  COUTYP4 = "County Type"
)
importance_df <- summary(cig_boost, n.trees = best_iter, plotit = FALSE)

# Add readable names
importance_df$Readable <- ifelse(importance_df$var %in% names(readable_names),
                                 readable_names[importance_df$var],
                                 importance_df$var)

library(ggplot2)
ggplot(importance_df, aes(x = reorder(Readable, rel.inf), y = rel.inf)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Alcohol use per year (Boosting)",
       x = "Variables",
       y = "Relative Influence") +
  theme_minimal(base_size = 14)


top_vars <- importance_df$var[1:6]  # Top 6 variables
par(mfrow = c(2, 3))
for (v in top_vars) {
  var_name <- ifelse(v %in% names(readable_names), readable_names[v], v)
  plot(cig_boost, i.var = v, n.trees = best_iter, main = var_name)
}
par(mfrow = c(1, 1))

```

